xwMOOC 딥러닝

### 2017-10-03 ng-tuning.Rmd
started deep learning project from coursera

---
layout: page
title: xwMOOC 딥러닝
subtitle: Structuring Machine Learning Projects
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    keep_md: yes
  pdf_document:
    latex_engine: xelatex
mainfont: NanumGothic
---

>>>>

---
layout: page
title: xwMOOC 딥러닝
subtitle: Improving Deep Neural Networks: Hyperparameter tuning, Regularization and Optimization
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    keep_md: yes
  pdf_document:
    latex_engine: xelatex
mainfont: NanumGothic
---
